\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of G dwarfs \vspace{-0.5cm}

### 2017-06-22 paper/ms.tex
more edits

% ------------------------
% nature summary paragraph
% ------------------------
% - a fully referenced paragraph, ideally of about 200 words, but certainly no
%   more than 300 words, aimed at readers in other disciplines.
% - This paragraph starts with a 2-3 sentence basic introduction to the field;
%   followed by a one-sentence statement of the main conclusions starting 'Here
%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
%   findings into general context so it is clear how the results described in
%   the paper have moved the field forwards.
% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
% ------------------------
\section{Summary}
{\bf \noindent
  Stars that are born together are expected to have same chemical compositions
  initially.
  Detailed chemical abundance studies of stars in wide binaries indeed reveal
  nearly identical chemistry in most
  cases\citep{Gratton:2001aa,Desidera:2004aa} as well as stars in open
  clusters\cite{Bovy:2016aa}.
  However, formation and evolution of different planetary systems around each
  star in a wide binary may eventually lead to a difference in compositions of
  the component stars' radiative and convective
  layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
  Wide binary systems of two twin-like stars are particularly useful
  as they are not subject to confusion with Galactic chemical evolution.
  A handful of wide binaries that show small differences in their surface
  chemical abundances have been reported so far
  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}.
  However, a convincing example is yet to be found.
  Here we report a comoving pair of bright sun-like stars, HD~240430 and HD~240429,
  with a significant difference ($\approx 0.2$~dex) in their chemical
  abundances that strongly suggests accretion of rocky planetary system in one
  of the stars within the last couple of billion years.
  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
  The two stars also show high Li abundance given their age of $\sim 4$ Gyr
  inferred from their stellar parameters.
  A prominent trend of element abundance enhancement with condensation temperature
  indicates the accreted material is rocky.
  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted
  $\approx 20$~\mearth\ of rocky material after birth selectively enhancing the
  refractory elements in its surface and convective envelope.
  The other star HD~240429, ``Krios'', may also have had a similar accretion
  event given its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  This pair of stars provides evidence that dynamical accretion of rocky planets
  happen during the lifetime of sun like stars.
}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone,
    normalized to \elem{H} (top) and \elem{Fe} (bottom).
    Lines are drawn for each star only to guide the eye.
    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to
    \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C},
    \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
    \label{fig:abundances}
  }
\end{figure}

\begin{table*}[htpb]
  \centering
  \begin{threeparttable}
  \caption{Astrometric and spectroscopic measurements of the pair\label{tab:t1}}
\begin{tabular}{ccccc}
\hline\hline
                        &                & \sunanalog\            & \bizarreone\           &               \\
Name                    & Units          & HD 240429              & HD 249439              & Uncertainties \\
\hline
Sp Type                 &                & G2                     & G0                     &               \\
R.A.\tnote{a}           & hh:mm:ss       & 23:51:55.21            & 23:52:09.42            &               \\
Dec.\tnote{a}           & dd:mm:ss       & 59:42:48.16            & 59:42:26.08            &               \\
2MASS $J$\tnote{a}      & mag            & $8.593 \pm 0.023$      & $8.415 \pm 0.026$      &               \\
$T_\mathrm{eff}$        & K              & 5878                   & 5803                   & 25            \\
$\log{g}$               &                & 4.43                   & 4.33                   & 0.028         \\
$v\sin{i}$              & \kms\          & 1.1                    & 2.5                    &               \\
$[\elem{Fe}/\elem{H}]$  &                & 0.01                   & 0.20                   & 0.010         \\
Age\tnote{b}            & Gyr            & $4.00_{-1.56}^{+1.51}$ & $4.28_{-1.03}^{+1.11}$ &               \\
$v_r$                   & \kms\          & $-21.2$                & $-21.2$                & 0.2           \\
$\varpi$\tnote{a}       & mas            & $9.35 \pm 0.24$        & $9.41 \pm 0.25$        &               \\
$\mu_\alpha^*$\tnote{a} & mas\,yr$^{-1}$ & $89.25 \pm 0.66$       & $89.41 \pm 0.69$       &               \\
$\mu_\delta$\tnote{a}   & mas\,yr$^{-1}$ & $-29.68 \pm 0.54$      & $-30.12 \pm 0.52$      &               \\
\hline 
\multicolumn{5}{c}{$T_c < 1200$~K} \\
\hline 
$A(\elem{Li})$\tnote{c} &                & $2.25$                 & $2.75$                 &               \\
$\elemH{C}$             &                & $0.00$                 & $0.09$                 & 0.026         \\
$\elemH{N}$             &                & $-0.06$                & $-0.01$                & 0.042         \\
$\elemH{O}$             &                & $0.01$                 & $0.09$                 & 0.036         \\
$\elemH{Na}$            &                & $-0.06$                & $-0.04$                & 0.014         \\
$\elemH{Mn}$            &                & $-0.03$                & $0.00$                 & 0.020         \\
\hline 
\multicolumn{5}{c}{$T_c > 1200$~K} \\
\hline 
$\elemH{Mg}$            &                & $0.01$                 & $0.19$                 & 0.012         \\
$\elemH{Al}$            &                & $0.01$                 & $0.21$                 & 0.028         \\
$\elemH{Si}$            &                & $0.00$                 & $0.16$                 & 0.008         \\
$\elemH{Ca}$            &                & $0.02$                 & $0.23$                 & 0.014         \\
$\elemH{Ti}$            &                & $0.02$                 & $0.20$                 & 0.012         \\
$\elemH{V}$             &                & $0.02$                 & $0.20$                 & 0.034         \\
$\elemH{Cr}$            &                & $0.01$                 & $0.17$                 & 0.014         \\
$\elemH{Fe}$            &                & $0.01$                 & $0.20$                 & 0.010         \\
$\elemH{Ni}$            &                & $-0.01$                & $0.21$                 & 0.014         \\
$\elemH{Y}$             &                & $0.04$                 & $0.26$                 & 0.030         \\

\end{tabular}
\begin{tablenotes}
\item [a] From \tgas.
\item [b] Derived in this work by isochrone fitting using the Yale-Yonsei model
  isochrones\cite{2013ApJ...776...87S}.
\item [c] Absolute abundances from Myles \etal, in prep.
\item All values are from \citet{2016ApJS..225...32B} unless otherwise noted.
\end{tablenotes}
\end{threeparttable}
\end{table*}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank.pdf}
  \caption{
    Comparing the observed abundance difference vs. \Tcondens\ rank
    to the expected change in solar surface abundance after adding $20$~\mearth\ of
    material with bulk Earth composition (\cite{mcdonough2001composition}).
    The assumed mass fraction in the convective zone is $0.03$.
    All metals are ranked by their \Tcondens\ for solar composition gas,
    and the condensation temperature may be read from the gray line and right y-axis,
    same as in \figname~\ref{fig:relabun_tcrank}.
    Locations of the elements measured for \bizarreone-\sunanalog\ pair are
    indicated by a vertical line and its symbol.
    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
    suggests that the abundance difference may be due to accretion of
    $20$~\mearth\ of rocky planetary material.
    The element \elem{Li} is off the plot and indicated with a red arrow
    (see text for details).
  }
  \label{fig:deltaxh_tcrank}
\end{figure}

The abundance differences show a strong increasing trend with condensation
temperature of elements.
In Figure~\ref{fig:deltaxh_tcrank},
we show the abundance difference between \bizarreone\ and \sunanalog\ ordered
by each element's equilibrium \Tcondens\ in solar system composition
gas\citet{2003ApJ...591.1220L}.
The five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile in all elements measured.
The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.

@@

We estimate that accretion of $\approx 15$~\mearth\ of rocky planets
in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
refractory elements as well as the surface Li abundance.
Because the anchor star, \sunanalog,
is very close in its properties (\teff, \logg, \feh, age) to the Sun,
we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
pre-accretion state of \bizarreone.
In Figure~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth
composition\cite{2003TrGeo...2..547M}.
A volatility trend that more volatile (low \Tcondens) elements are more
depleted in the Earth relative to CI or other carbonaceous chondrites
has long been known\cite{mcdonough2001composition}.
This trend is presumed to be closely related to the formation of terrestrial
planets and, in particular to the radial temperature gradient in a
protoplanetary disk.
The trend resulting from adding $15$~\mearth\ of bulk Earth
provides an overall good match to the observed $\Delta\elemH{X}$,
suggesting that the refractory-enhanced star, \bizarreone\,
accreted $15$~\mearth more of rocky planetary material than \sunanalog.

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium on the star's surface.
For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex (which
is indicated as an upward arrow in \figname~\ref{fig:toycalc}).
Incidentally, the star under examination, \bizarreone, has an age (informed by
stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with $1.6$~dex
enhancement in its \elem{Li}.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \cite{jmlithium})
approximately $1.65$~dex higher than the solar value of $1.1$~dex
(\todo{needs reference}).
Furthermore, this implies that the accretion event should have happened very
recently, or at least within the \elem{Li} depletion time ($\lesssim 1$~Gyr).

What about \sunanalog?
Considering its age of $4.00_{-1.56}^{+1.51}$~Gyr, \sunanalog\ is also enhanced
in \elem{Li} compared to other stars of similar ages by $\approx 1$~dex.
This enhancement puts an upper limit on the accreted mass to be
$\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
(\cite{mcdonough2001composition}).
Unlike \bizarreone, we cannot know the pre-accretion abundances of
\sunanalog.\footnote{
  Strictly speaking, we can never know the pre-accretion abundances
  for \bizarreone\ either.
  We only have an {\it approximate} idea that this is not far from a solar-twin
  star \sunanalog, and because the deviation from this ``anchor'' star is
  large, it is reasonable to consider accretion by the Sun.
  In reality, \sunanalog\ may as well have had its own accretion history,
  which indeed seems to be the case according to its \elem{Li} abundance.
}
However, we note that the span of abundance difference between highly volatile
elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
as \elem{Fe} expected from accreting $4$~\mearth\ to the Sun is $\approx
0.05$~dex.
This is comparable to the abundance difference between N, Na and Fe in
\sunanalog.
It is also interesting that \sunanalog\ shows a deficit in the same volatile
and moderately volatile elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
\elem{Mn}) relative to Fe as in \bizarreone.
Thus, we conclude that \sunanalog\ is also likely to have had a similar
accretion event, but the amount of accretion was at least 5 time
smaller than \bizarreone.

%TODO: augment this paragraph
% - more geochemical study references
%We stress that while the calculation carried out is useful in
%an order-of-magnitude sense, further investigation of each of the simplifying
%assumptions made is warranted.
%In addition, the composition of bulk Earth has some uncertainties.
%For example, the reported bulk Earth concentration of the siderphile element
%\elem{Mn}, varies from $800$ to $1700$~ppm (\cite{1998psc..book.....L}).
%While the latter value from \cite{mcdonough2001composition} has been used in
%our calculation, the former value would bring the observed $\Delta\elemH{Mn}$
%to an even closer agreement.
%Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
%\elem{Li} for \bizarreone\ is remarkable.

Given that the two stars must have engulfed planets,
it is likely that they have not destroyed all of their planets.
Any surviving planet around the stars must be giants.
Fortunately, discovery of giant eccentric planets using astrometric jitter is in the sweet spot
for Gaia.
The two stars have not been included in any publicly released data from planet
search programs.
If both stars have accreted planetary material, it would be very interesting to
search for the existence and architectures of the planetary systems left
behind.

@@

\section*{Supplementary Information}

\subsection*{Proximity in phase-space coordinates}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
  \end{center}
  \caption{%
    Differences in posterior samples over Galactocentric phase-space coordinates
    for the two stars \sunanalog\ and \bizarreone.
    \label{fig:dxdv}}
\end{figure}

@@

\subsection*{Stellar Ages and Coevality}

@@

\subsection*{Chemical Inhomogeneity in Star Formation}
\label{sub:chemical_inhomogeneity_in_star_formation}

Assuming that the two stars were born together, one possibility to
explain the chemical difference is that there was chemical inhomogeneity within
the birth cloud.
However, there is already ample evidence against such a scenario.
First, none of the other seven similar wide binaries examined in
\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
$\elem{O}$, and some pairs show a difference in particular elements as large as
$\approx 0.15$~dex.
The median and maximum \feh\ difference between component stars in the other
seven pairs is $0.02$~dex and $0.09$~dex, respectively.
The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
(\figname~\ref{fig:deltaXH}).
This is consistent with the findings of \citealt{Desidera:2004aa}, who examined
23 wide binaries of late F to K dwarfs, and found most pairs show a difference
in \feh\ less than $0.02$~dex and none larger than $0.07$~dex.
Similarly, \citealt{Gratton:2001aa} found that four out of six equal mass
binaries have the same chemical composition with $\gtrsim 0.01$~dex
uncertainties.
Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
not likely due to chemical inhomogeneity in the birth cloud.

\subsection*{Estimating the accreted masses}

>>>>

% ------------------------
% nature summary paragraph
% ------------------------
% - a fully referenced paragraph, ideally of about 200 words, but certainly no
%   more than 300 words, aimed at readers in other disciplines.
% - This paragraph starts with a 2-3 sentence basic introduction to the field;
%   followed by a one-sentence statement of the main conclusions starting 'Here
%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
%   findings into general context so it is clear how the results described in
%   the paper have moved the field forwards.
% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
% ------------------------
\section{Summary}
{\bf \noindent
  Stars that are born together are expected to have same chemical compositions
  initially.
  Detailed chemical abundance studies of stars in wide binaries indeed reveal
  little to no differences in most cases\citep{Gratton:2001aa,Desidera:2004aa}.
  However, formation and evolution of different planetary systems around each
  star in a wide binary may eventually lead to a difference in chemical
  abundances of the component stars' radiative and convective
  layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
  Wide binary systems of two twin-like stars are particularly useful since such
  chemical signature may be more easily detectable as abundance differences,
  free from dependence on stellar parameters or confusion with Galactic chemical
  evolution.
  A handful of wide binaries that show small differences ($0.03$--$0.1$~dex)
  in their surface chemical abundances have been reported so far
  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}.
  However, a convincing example is yet to be found.
  %
  Here we report a comoving pair of bright sun-like stars, HD~240430 and HD~240429,
  hereafter ``\bizarreone'' and ``\sunanalog'',
  with a significant difference ($\approx 0.2$~dex) in their chemical
  abundances that strongly suggests massive accretion of rocky planetary system in one
  of the stars within the last billion years.
  The more metal-rich of the two, \bizarreone, shows an enhancement of refractory
  elements by $\approx 0.2$~dex but not as large
  an enhancement of (moderately) volatile elements.
  The two stars also show high \elem{Li} abundance given their age of $\sim 4$ Gyr
  inferred from their stellar parameters.
  We suggest that the star \bizarreone, recently accreted
  $\approx 15$~\mearth\ of rocky material selectively enhancing the
  refractory elements in its surface and convective envelope.
  The other star, \sunanalog, may also have had a similar accretion
  event given its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  This pair of stars provides evidence that dynamical accretion of rocky planets
  happen during the lifetime of sun like stars.
}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair, 
    \bizarreone\ (red circles) and \sunanalog\ (blue squares).
    Lines are drawn for each star only to guide the eye.
    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to
    \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C},
    \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
    \label{fig:abundances}
  }
\end{figure}

\begin{table*}[htpb]
  \centering
  \begin{threeparttable}
  \caption{Astrometric and spectroscopic measurements of the pair\label{tab:t1}}
\begin{tabular}{ccccc}
\hline\hline
                        &                & \sunanalog\            & \bizarreone\           &               \\
Name                    & Units          & HD 240429              & HD 249439              & Uncertainties \\
\hline
Sp Type                 &                & G2                     & G0                     &               \\
R.A.\tnote{a}           & hh:mm:ss       & 23:51:55.21            & 23:52:09.42            &               \\
Dec.\tnote{a}           & dd:mm:ss       & 59:42:48.16            & 59:42:26.08            &               \\
2MASS $J$\tnote{a}      & mag            & $8.593 \pm 0.023$      & $8.415 \pm 0.026$      &               \\
$T_\mathrm{eff}$        & K              & 5878                   & 5803                   & 25            \\
$\log{g}$               &                & 4.43                   & 4.33                   & 0.028         \\
$v\sin{i}$              & \kms\          & 1.1                    & 2.5                    &               \\
$[\elem{Fe}/\elem{H}]$  &                & 0.01                   & 0.20                   & 0.010         \\
Age\tnote{b}            & Gyr            & $4.00_{-1.56}^{+1.51}$ & $4.28_{-1.03}^{+1.11}$ &               \\
$v_r$                   & \kms\          & $-21.2$                & $-21.2$                & 0.2           \\
$\varpi$\tnote{a}       & mas            & $9.35 \pm 0.24$        & $9.41 \pm 0.25$        &               \\
$\mu_\alpha^*$\tnote{a} & mas\,yr$^{-1}$ & $89.25 \pm 0.66$       & $89.41 \pm 0.69$       &               \\
$\mu_\delta$\tnote{a}   & mas\,yr$^{-1}$ & $-29.68 \pm 0.54$      & $-30.12 \pm 0.52$      &               \\
\hline 
\multicolumn{5}{c}{$T_c < 1200$~K} \\
\hline 
$A(\elem{Li})$\tnote{c} &                & $2.25$                 & $2.75$                 &               \\
$\elemH{C}$             &                & $0.00$                 & $0.09$                 & 0.026         \\
$\elemH{N}$             &                & $-0.06$                & $-0.01$                & 0.042         \\
$\elemH{O}$             &                & $0.01$                 & $0.09$                 & 0.036         \\
$\elemH{Na}$            &                & $-0.06$                & $-0.04$                & 0.014         \\
$\elemH{Mn}$            &                & $-0.03$                & $0.00$                 & 0.020         \\
\hline 
\multicolumn{5}{c}{$T_c > 1200$~K} \\
\hline 
$\elemH{Mg}$            &                & $0.01$                 & $0.19$                 & 0.012         \\
$\elemH{Al}$            &                & $0.01$                 & $0.21$                 & 0.028         \\
$\elemH{Si}$            &                & $0.00$                 & $0.16$                 & 0.008         \\
$\elemH{Ca}$            &                & $0.02$                 & $0.23$                 & 0.014         \\
$\elemH{Ti}$            &                & $0.02$                 & $0.20$                 & 0.012         \\
$\elemH{V}$             &                & $0.02$                 & $0.20$                 & 0.034         \\
$\elemH{Cr}$            &                & $0.01$                 & $0.17$                 & 0.014         \\
$\elemH{Fe}$            &                & $0.01$                 & $0.20$                 & 0.010         \\
$\elemH{Ni}$            &                & $-0.01$                & $0.21$                 & 0.014         \\
$\elemH{Y}$             &                & $0.04$                 & $0.26$                 & 0.030         \\
\hline
\end{tabular}
\begin{tablenotes}
\item [a] From \tgas.
\item [b] Derived in this work by isochrone fitting using the Yale-Yonsei model
  isochrones\cite{2013ApJ...776...87S}.
\item [c] Absolute abundances from Myles \etal, in prep.
%\item All values are from \citet{2016ApJS..225...32B} unless otherwise noted.
\end{tablenotes}
\end{threeparttable}
\end{table*}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank.pdf}
  \caption{
    Comparing the observed abundance difference (blue circles) to the expected
    change in solar surface abundance after adding $15$~\mearth\ of material
    with bulk Earth composition\cite{2003TrGeo...2..547M} (black open and
    filled circles).
    The assumed mass fraction in the convective zone is $0.02$.
    All astronomical metals are ordered by their \Tcondens\ for solar
    composition gas on the $x$-axis.
    For the predictions, we highlight elements measured for \bizarreone-\sunanalog\ pair
    in filled circles, while those without a measurement are left open.
    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
    suggests that the abundance difference may be due to accretion of
    $15$~\mearth\ of rocky planetary material.
    The element \elem{Li} is off the plot and indicated in the inset.
  }
  \label{fig:deltaxh_tcrank}
\end{figure}

The abundance differences show a strong increasing trend with condensation
temperature ($T_C$) of elements.
In Figure~\ref{fig:deltaxh_tcrank},
we show the abundance difference between \bizarreone\ and \sunanalog\ ordered
by each element's equilibrium \Tcondens\ in solar system composition
gas\cite{2003ApJ...591.1220L}.
The five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile in all elements measured.
The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.

@@

We estimate that accretion of $\approx 15$~\mearth\ of rocky planets
in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
refractory elements as well as the surface Li abundance.
Because the anchor star, \sunanalog,
is very close in its properties (\teff, \logg, \feh, age) to the Sun,
we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
pre-accretion state of \bizarreone.
In Figure~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth
composition\cite{2003TrGeo...2..547M} assuming that 2\% of the Sun's mass
is in its convective zone\cite{Pinsonneault:2001aa}.
A volatility trend that more volatile (low \Tcondens) elements are more
depleted in the Earth relative to CI or other carbonaceous chondrites
has long been known\cite{mcdonough2001composition}.
This trend is presumed to be closely related to the formation of terrestrial
planets and, in particular to the radial temperature gradient in a
protoplanetary disk.
The trend resulting from adding $15$~\mearth\ of bulk Earth provides an overall
good match to the observed $\Delta\elemH{X}$, suggesting that the
refractory-enhanced star, \bizarreone\, accreted $\approx 15$~\mearth\ more of
rocky planetary material than \sunanalog.

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium on the star's surface.
For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex
(see inset of Figure~\ref{fig:deltaxh_tcrank}).
Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
stellar parameters) very close to the Sun ($\sim 4$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with $1.6$~dex
enhancement in its \elem{Li}.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep)
approximately $1.65$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
Furthermore, this implies that the accretion event should have happened
recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).

What about \sunanalog?
Considering its age of $4.00_{-1.56}^{+1.51}$~Gyr, \sunanalog\ is also enhanced
in \elem{Li} compared to other stars of similar ages by $\approx 1$~dex.
This enhancement puts an upper limit on the accreted mass to be
$\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
\cite{mcdonough2001composition}.
Unlike \bizarreone, we cannot know the pre-accretion abundances of
\sunanalog.\footnote{
  Strictly speaking, we can never know the pre-accretion abundances
  for \bizarreone\ either.
  We only have an {\it approximate} idea that this is not far from a solar-twin
  star \sunanalog, and because the deviation from this ``anchor'' star is
  large, it is reasonable to consider accretion by the Sun.
  In reality, \sunanalog\ may as well have had its own accretion history,
  which indeed seems to be the case according to its \elem{Li} abundance.
}
However, we note that the span of abundance difference between highly volatile
elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
as \elem{Fe} expected from accreting $4$~\mearth\ to the Sun is $\approx
0.05$~dex.
This is comparable to the abundance difference between N, Na and Fe in
\sunanalog.
It is also interesting that \sunanalog\ shows a deficit in the same volatile
and moderately volatile elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
\elem{Mn}) relative to Fe as in \bizarreone.
Thus, we conclude that \sunanalog\ is also likely to have had a similar
accretion event, but the amount of accretion was at least 5 time
smaller than \bizarreone.

What triggered the planet engulfment in the two comoving stars
within the last Gyr remains unclear.
A possibility is that a fly-by interaction with a field star could have
triggered eccentricity excitation of outer planets around each star, which may
have propagated inward through planet-planet scattering, making inner rocky planets
to be accreted\cite{Malmberg:2011aa}.
If this is the case, there may be surviving highly eccentric giant planets that are
potentially detectable with future data releases of \gaia.
The two stars have not been included in any publicly released data from planet
search programs.
If both stars have accreted planetary material, it would be very interesting to
search for the existence and architectures of the planetary systems left
behind.

@@

\section{Supplementary Information}

\subsection{Proximity in phase-space coordinates}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
  \end{center}
  \caption{%
    Differences in posterior samples over Galactocentric phase-space coordinates
    for the two stars, \bizarreone\ and \sunanalog.
    \label{fig:dxdv}}
\end{figure}

@@

\subsection{Stellar Ages and Coevality}

@@

\subsection{Alternative Scenarios}

\subsubsection{Chemical Inhomogeneity in Star Formation}
\label{sub:chemical_inhomogeneity_in_star_formation}

Assuming that the two stars were born together, one alternative possibility to
explain the chemical difference between the two stars is that there was
chemical inhomogeneity within the birth cloud.
However, there is already ample evidence against such a scenario.
First, none of the other seven similar wide binaries examined
with the same measurement pipeline\cite{2016ApJS..225...32B}
show the same level of differences in abundances.
Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
$\elem{O}$, and some pairs show a difference in particular elements as large as
$\approx 0.15$~dex.
The median and maximum \feh\ difference between component stars in the other
seven pairs is $0.02$~dex and $0.09$~dex, respectively.
The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
(\figname~\ref{fig:deltaXH}).
This is consistent with similar previous studies\cite{Gratton:2001aa,Desidera:2004aa}.
Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
not likely due to chemical inhomogeneity in the birth cloud.

\subsection{Estimating the accreted masses}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank_vari.pdf}
  \caption{Expected differences in solar abundances after adding
    varying mass of bulk Earth material.
    Elements are ordered by their $T_C$ on $x$-axis, same as
    Figure~\ref{fig:deltaxh_tcrank}.
    The solid and dashed lines assume $f_\mathrm{CZ}=0.02$ and $f_\mathrm{CZ} =
    0.03$ respectively.
    For each $f_\mathrm{CZ}$, we show expected $\Delta\elemH{X}$
    for adding 5, 10, 15, 20, 25~\mearth\ of bulk Earth (from bottom to top).
  }
  \label{fig:vari}
\end{figure}

We estimate how much mass of rocky material is needed to explain an increment
of $\approx 0.2$~dex in refractory elements observed in \bizarreone\ relative
to \sunanalog\cite{Mack:2014aa,Mack:2016aa}.
Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
and \feh\ is very close to those of the Sun ($\Delta T_\mathrm{eff} \approx XX$,
$\delta\logg \approx XX$, and $\Delta\feh \approx 0$),
we may approximate the pre-accretion abundances of \bizarreone\ with the Sun.
We carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
under these simplifying assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
  \item The surface abundance of the star has been altered only by the
    accretion event(s).
\end{itemize}
We take the solar abundances\cite{Asplund:2009aa}, $\elemH{X}$, of element \elem{X}
which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in e.g., atomic mass unit.
Assuming that the added material has a total mass $M_\mathrm{add}$, and the
mass fraction in each element $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We take the composition of bulk Earth\cite{mcdonough2001composition}
as a proxy for rocky planet composition. We adopt $f_\mathrm{CZ} = 0.02$ for
the fraction of mass in the convective zone\cite{Pinsonneault:2001aa}.

The estimate of accreted mass depends sensitively on $f_\mathrm{CZ}$ and the
mass of the star which are difficult quantities to constrain directly through
data.
While we adopt $(f_\mathrm{CZ},\,M) = (0.02, 1~M_\odot)$, we show the
expected changes in $\Delta\elemH{X}$ for $f_\mathrm{CZ}=0.03$ in
Figure~\ref{fig:vari}.

We stress that while the calculation carried out is useful in
an order-of-magnitude sense, further investigation of each of the simplifying
assumptions made is warranted.
In addition, the composition of bulk Earth has some uncertainties.
For example, the reported bulk Earth concentration of \elem{Mn}, varies from
$800$ to $1700$~ppm\cite{1998psc..book.....L,mcdonough2001composition,2003TrGeo...2..547M}
largely due to uncertainties in the composition of the Earth's core.
Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
\elem{Li} for \bizarreone\ is remarkable.
